---
title: "Example Workflow for PEPR DeGAUSS Containers"
date: "7/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(knitr)
library(kableExtra)
```

# Introduction

This is an example of the workflow a PEPR study site might use to add geomarkers to their data with [DeGAUSS](https://github.com/cole-brokamp/DeGAUSS). 

In steps 2 through 5: 

+ A DeGAUSS container is used to add geomarker(s) to the input file (columns added in each step are highlighted in gray).
+ The input file is the CSV created in the previous step, and the output file will be the input in the next step.

# Step 0: Install Docker

See the [Installing Docker](https://github.com/cole-brokamp/DeGAUSS/wiki/Installing-Docker) wiki.

# Step 1: Preparing Your Input File

The input file must be a CSV file with a column containing an address string. Other columns may be present and will be returned in the output file, but should be kept to a minimum to reduce file size.

An example input CSV file (called `my_address_file.csv`) might look like:

```{r}
my_adds_geo <- read_csv("./example_data/my_address_file_geocoded.csv")

sample_ids <- c("11200020024", "54000600136", "13100070229")
my_adds_geo <- filter(my_adds_geo, id %in% sample_ids)

my_adds_geo %>% 
  select(-(bad_address:dep_index)) %>% 
  kable() %>% 
  kable_styling(full_width = FALSE, bootstrap_options = "striped")
```

Refer to the DeGAUSS [geocoding wiki](https://github.com/cole-brokamp/DeGAUSS/wiki/Geocoding-with-DeGAUSS) for more information about the input file and address string formatting.

# Step 2: Geocoding and Deprivation Index

Open a shell (i.e., terminal on Mac or CMD on Windows). We will use this shell for the rest of the steps in this example.

Navigate to the directory where the CSV file to be geocoded is located. See [here](http://linuxcommand.org/lc3_lts0020.php) for help on navigating a filesystem using the command line.

For those unfamiliar with the command line, the simplest approach might be to put the file to be geocoded on the desktop and then navigate to your desktop folder after starting the Docker Quickstart Terminal with `cd Desktop`.

Example call:

```
docker run --rm=TRUE -v "$PWD":/tmp degauss/cchmc_batch_geocoder my_address_file.csv
```

Replace `my_address_file.csv` with the name of the CSV file to be geocoded and run the call in the shell.

**Note for Windows Users:** In this and all following docker calls in this example, replace `"$PWD"` with `"%cd%"`.

The **output file** is written to the same directory and in our example, will be called `my_address_file_geocoded.csv`.

Example output:

```{r}
my_adds_geo %>% 
  kable() %>% 
  kable_styling(full_width = FALSE, bootstrap_options = "striped") %>% 
  column_spec(3:17, bold = T, color = "white", background = "gray", include_thead = TRUE) %>% 
  scroll_box(width = "900px", height = "300px")
```

# Step 3: Distance to Major Roadway

Example call:

```
docker run --rm=TRUE -v "$PWD":/tmp degauss/dist_to_major_roadway my_address_file_geocoded.csv
```

Replace `my_address_file_geocoded.csv` with the name of the geocoded CSV file created in Step 2 and run.

The **output file** is written to the same directory and in our example, will be called `my_address_file_geocoded_disttomajorroadway.csv`.

Example output:

```{r}
dist_road <- read_csv("./example_data/my_address_file_geocoded_disttomajorroadway.csv") %>% 
    filter(id %in% sample_ids)

dist_road%>% 
  kable() %>% 
  kable_styling(full_width = FALSE, bootstrap_options = "striped") %>% 
  column_spec(16, bold = T, color = "white", background = "gray", include_thead = TRUE) %>% 
  scroll_box(width = "900px", height = "300px")
```

# Step 4: Drive Time and Distance to Care Center

Example call: 

```
docker run --rm -v "$PWD":/tmp degauss/pepr_drivetime:0.4 my_address_file_geocoded_disttomajorroadway.csv cchmc
```

Replace `my_address_file_geocoded_disttomajorroadway.csv` with the name of the CSV file created in Step 3, and replace `cchmc` with the abbrevation for your care center (see [list](https://github.com/cole-brokamp/PEPR_drivetime)) and run.

The **output file** is written to the same directory and in our example, will be called `my_address_file_geocoded_disttomajorroadway_pepr_drivetime_cchmc.csv`.

Example output:

```{r}
drivetime <- read_csv("./example_data/my_address_file_geocoded_pepr_drivetime_cchmc.csv") %>% 
  filter(id %in% sample_ids) %>% 
  select(id, drive_time, distance)

drivetime <- dist_road %>% 
  right_join(drivetime, by="id")

drivetime %>% 
  kable() %>% 
  kable_styling(full_width = FALSE, bootstrap_options = "striped") %>% 
  column_spec(19:20, bold = T, color = "white", background = "gray", include_thead = TRUE) %>% 
  scroll_box(width = "900px", height = "300px")
```

# Step 5: Greenspace

Example call: 

```
docker run --rm -v "$PWD":/tmp degauss/pepr_greenspace:0.1 my_address_file_geocoded_disttomajorroadway_pepr_drivetime_cchmc.csv
```

Replace `my_address_file_geocoded_disttomajorroadway_pepr_drivetime_cchmc.csv` with the name of the CSV file created in Step 4 and run.

The **output file** is written to the same directory and in our example, will be called `my_address_file_geocoded_disttomajorroadway_pepr_drivetime_cchmc_pepr_greenspace.csv`.

Example output:

```{r}
greenspace <- read_csv("./example_data/my_address_file_geocoded_pepr_greenspace.csv") %>% 
  filter(id %in% sample_ids) %>% 
  select(id, evi_500:evi_2500)

greenspace <- drivetime %>% 
  right_join(greenspace, by="id")

greenspace %>% 
  kable() %>% 
  kable_styling(full_width = FALSE, bootstrap_options = "striped") %>% 
  column_spec(21:23, bold = T, color = "white", background = "gray", include_thead = TRUE) %>% 
  scroll_box(width = "900px", height = "300px")
```

# Step 6: Crime

Example call: 

```
docker run --rm -v "$PWD":/tmp degauss/pepr_drivetime/pepr_crime:0.1 my_address_file_geocoded_disttomajorroadway_pepr_drivetime_cchmc_pepr_greenspace.csv
```

Replace `my_address_file_geocoded_disttomajorroadway_pepr_drivetime_cchmc_pepr_greenspace.csv` with the name of the CSV file created in Step 5 and run.

The **output file** is written to the same directory and in our example, will be called `my_address_file_geocoded_disttomajorroadway_pepr_drivetime_cchmc_pepr_greenspace_pepr_crime.csv`.

Example output:


